Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-08 3_background/background.tex
no message

In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch thesis and the aim of constructing a necessary background.

>>>>

In this section process discovery methods and mismatch patterns are presented within the  the scope of this resarch and the aim of constructing a necessary background.

### 2015-09-08 5_results_discussions/loan-application-process/loan-application-process.tex
no message

\subsection{Loan Application Process}
\label{subsec:loan-app-process}
\textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute. These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}. In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this thesis study is be applied.

>>>>

\subsection{Loan Application Process}
\label{subsec:loan-app-process}
\textit{Loan Application Process} dataset is synthetically created and consists of four variants of a simple loan application in a financial institute. These event logs are used to test different approaches of discovering a configurable process model from a collection of event logs \cite{buijs2014flexible}. In this dataset there are a total of 475 cases and 2440 events with a fairly even distribution between variants and these variants are used as organizational logs and the methodology presented in this study is be applied.
